On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-03-25 engineering.tex
def channel and port

While \emph{agents} and \emph{communication} between agents are described and
defined in Section~\ref{sec:theory}, both the concepts of \emph{port},
\emph{channel}, \emph{functional and physical architecture}, and
\emph{functional block} have not yet been defined with respect to the $\abf$-theory.
Informally, a channel identifies the place where the communication takes place.
In this work we only consider mono-directional channels and communication but the 
extension to bi-directional channel can be considered as the union of two
unidirectional channels.

\begin{definition}{\bf mono-directional channel --}\label{def:monochannel}
	A mono-directional channel is defined by the message sent and received
	over the channel. Given two agents $s$ (sender) and $r$ (receiver) a
	mono-directional channel $s \rightarrow r$ defines the sending of
	information between $s$ and $r$. 
	%$\assertion{s}{r}$ is defined as a (improper) subset of the assertions of $s$, i.e.
	%$\pp{\assertion{s}{r}}{\assertion{s}}
	%PP(A λ S ,λ R , A λ S ) ∨ EQ(A λ S ,λ R , A λ S ) (since λ S may
	%communicate with other agents).  The receipt of messages over a
	%mono-directional channel is defined as the topolog- ical boundary B S
	%,R (improper) subset of the beliefs of the receiver (i.e., the beliefs
	%generated by the message exchange and by computations over the set of
	%beliefs): PP(B S ,R , B R ) ∨ EQ(B S ,R , B R ).
\end{definition}

\begin{definition}{\bf \fix{mr}{informal Input or Output Port} --}\label{def:port} 
	Ports are agents with the following predefined behavior: an input-port
	changes the type of information from assertion to belief while an
	output-port from belief to assertion; forwarding information from the
	outside of an agent's boundary to the inside (input-port) or vice versa
	(output-port).
\end{definition}

>>>>

While \emph{agents} and \emph{communication} between agents are described and
defined in Section~\ref{sec:theory}, both the concepts of \emph{port},
\emph{channel}, \emph{functional and physical architecture}, and
\emph{functional block} have not yet been defined with respect to the
$\abf$-theory.  Informally, a channel identifies the place where the
communication takes place.  In this work we only consider mono-directional
channels and communication but the extension to bi-directional channel can be
considered as the union of two unidirectional channels. A mono-directional
channel is defined by the assertions sent or received (over the channel).

\begin{definition}{\bf mono-directional channel --}\label{def:monochannel}
	Given two agents $s$ (sender) and $r$ (receiver) a
	mono-directional channel $s \rightarrow r$ is defined as the union of all the assertions 
	$\rassert{s}{r}$ sent by $s$ to $r$ ($\assertionRegion_s$) and received by $r$ from $s$ ($\assertionRegion_r$). 
\end{definition}
The \emph{quality of a mono-directional} channel is defined as the 
$\rcc$ relation between the assertions made by the sender and the ones received by the receiver, i.e. $\Rcc{s}{r}$.

\begin{definition}{\bf Input or Output Port --}\label{def:port} 
	Ports are agents with the following predefined behavior: an input-port changes
	the type of information from assertion from a sender $s$ to an agent $a$,
	$\rassert{s}{a}$ to belief of the agent $a$ ($\beliefRegion_a$) while an
	output-port from belief to assertion; forwarding information from the outside
	of an agent's boundary to the inside (input-port) or vice versa (output-port). 
\end{definition}
The \emph{quality of a port} is determined by the $\rcc$ relation between the 
assertions received or sent and the belief, i.e. $\Rcc{\assertionRegion_s}{\beliefRegion_a}$ for the input-port
or $\Rcc{\assertionRegion_r}{\beliefRegion_a}$.

\begin{definition}{\bf Secure Input Port --}\label{def:secport}
	A secure input port allows information as incoming assertions to flow
	from a sender $s$ to the behavior of the recipient $a$ (agent).  If $p_I$ is a secure input port,
	$\world\models\varphi$, and $\varphi\in\assertionRegion_s$ where $s$
	has the only input port $p_I$, $\world'\models\beliefRegion_a$ and $\varphi\in\beliefRegion_a$.
\end{definition}
From this definition, it follows that there exist only the following types of insecure port in RCC5:
\begin{itemize}
	\item \emph{drop port} ($s\circ\rightarrow a$), where assertions reaches the port but do not pass the boundary of the agent (i.e. do not become belief of the agent)
	\item \emph{insertion port} ($s\rightarrow\bullet a$), where some new information is believed by $a$ as incoming from the port but $s$ didn't send it
	\item \emph{injection port} ($s\circ\rightarrow\bullet a$), where information coming from $s$ is substituted with new information which becomes believed by $a$
	\item \emph{selective port} ($s\hookrightarrow a$), where some
		information passes the port while other is either dropped
		($s\circ\hookrightarrow a$), inserted
		($s\hookrightarrow\bullet a$), or injected
		($s\circ\hookrightarrow\bullet a$)
\end{itemize}

\begin{proof}

\end{proof}
